---
title: "Scratchpad"
author: "Manojkumar Parmar"
date: "1/23/2017"
output: 
  pdf_document: 
    number_sections: yes
    toc: yes
    toc_depth: 5
  html_document: 
    number_sections: yes
    theme: journal
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Environment
```{r loadlibraries, echo=TRUE, message=FALSE, warning=FALSE}
#load libraries
library(datasets)
library(tm)
library(SnowballC)
library(RWeka)
library(ggplot2)
library(gridExtra)
library(wordcloud)
#cleanup environmant
rm(list = ls())
cat("\014")
```


# Procesing Data

## Fetching
```{r Fetchingdata, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
if(! file.exists("./00_Data/All_Read.RData")){
        tweetFile <- file("./00_Data/final/en_US/en_US.twitter.txt", "r")
        blogFile <- file("./00_Data/final/en_US/en_US.blogs.txt","r")
        newsFile <- file("./00_Data/final/en_US/en_US.news.txt","r")
        contentTweet <- readLines(tweetFile)
        contentBlog <- readLines(blogFile)
        contentNews <- readLines(newsFile)
        close(tweetFile)
        close(blogFile)
        close(newsFile)
        save.image("./00_Data/All_Read.RData")
}else{
        load("./00_Data/All_Read.RData")
        
}
```

Dataset is too big hence & only $1$% of tweet data, $1.5$% of blog data and $1.5$% of news data is used. Also combined version of all data is also prepared.
```{r resize, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
set.seed(1)
contentTweet <- sample(contentTweet, length(contentTweet)* 0.01)
contentBlog <- sample(contentBlog, length(contentBlog) * 0.015)
contentNews <- sample(contentNews, length(contentNews) * 0.015)
contentPart <-c(contentTweet, contentBlog, contentNews)
```

## Cleaning Data

Cleaning Function comprising multiple elements

- Removal of Punctuation
- Removal of Numbers
- Removal of URLs &  Email id
- Removal of Twitter tags & username
- Removal of profane words ([DataSet1]("https://raw.githubusercontent.com/shutterstock/List-of-Dirty-Naughty-Obscene-and-Otherwise-Bad-Words/master/en"), [DataSet2]("http://www.frontgatemedia.com/new/wp-content/uploads/2014/03/Terms-to-Block.csv"))
- Removal of English stop words
- Removal of White spaces
- Stemming of documents

```{r processingfunc, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
tm_pre_process <- function(data) {
        library(tm)
        
        # Create patterns to elimina special code and other patterns
        # URLs
        urlPat <- function(x)
                gsub("(ftp|http)(s?)://.*\\b", "", x)
        # Emails
        emlPat <-
                function(x)
                        gsub("\\b[A-Z a-z 0-9._ - ]*[@](.*?)[.]{1,3} \\b", "", x)
        # Twitter tags
        tt <- function(x)
                gsub("RT |via", "", x)
        # Twitter Usernames
        tun <- function(x)
                gsub("[@][a - zA - Z0 - 9_]{1,15}", "", x)
        #Remove profane words
        pwdat <-
                read.table(
                        "./00_Data/final/profane_words/en_bws.txt",
                        header = FALSE,
                        sep = "\n",
                        strip.white = TRUE
                )
        names(pwdat) <- "Profane Words"
        pwdat1 <- read.csv("./00_Data/final/profane_words/Terms-to-Block.csv")
        pwdat1 <- pwdat1[-(1:3), 2]
        pwdat1 <- gsub(",","",pwdat1)
        stpWrdList <- c(as.character(pwdat[,1]), 
                        pwdat1,
                        stopwords("english")
                        )
        
        corpusTitle = Corpus(VectorSource(data))
        corpusTitle = tm_map(corpusTitle, tolower)
        corpusTitle = tm_map(corpusTitle, PlainTextDocument)
        corpusTitle = tm_map(corpusTitle, removePunctuation)
        corpusTitle = tm_map(corpusTitle, removeNumbers)
        corpusTitle = tm_map(corpusTitle, urlPat)
        corpusTitle = tm_map(corpusTitle, emlPat)
        corpusTitle = tm_map(corpusTitle, tt)
        corpusTitle = tm_map(corpusTitle, tun)
        corpusTitle = tm_map(corpusTitle, removeWords, stpWrdList)
        corpusTitle = tm_map(corpusTitle, stemDocument)
        corpusTitle = tm_map(corpusTitle, stripWhitespace)
        corpusTitle
}
```

Using above mentioned pre processing function, lets clean all corpus.
```{r processingdata, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
corpusTweet <- tm_pre_process(contentTweet)
corpusNews <- tm_pre_process(contentNews)
corpusBlog <- tm_pre_process(contentBlog)
corpusPart <- tm_pre_process(contentPart)
```

## Tokenization of data

Tokenization function generates dataset based on given token count. Multiple token count is refered as per below

- 1 token : UniGram
- 2 token : BiGram
- 3 token : TriGram
- 4 token : QuadGram

Tokenization function also provides top enties where maximum freuqncy of tokens are present.

```{r tokenfunc, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
#tokenizer function
tokenizer <- function(corpusTitle, tokenCount) {
        token <- NGramTokenizer(
                corpusTitle,
                Weka_control(
                        min = tokenCount,
                        max = tokenCount,
                        delimiters = " \\r\\n\\t.,;:\"()?!"
                )
        )
        token
}

#function to generate top values from given token count
gramTopCount <- function(corpusTitle, tokenCount, TopCount = 0) {
        token <- tokenizer(corpusTitle, tokenCount)
        gram <- data.frame(table(token))
        gram <- gram[order(gram$Freq, decreasing = T), ]
        rownames(gram) <- NULL
        colnames(gram) <- c("Word", "Frequency")
        if(TopCount > 0){
                gram <- gram[1:TopCount, ]
                print(gramPlot(gram))
        }
        gram
}
```

Using above function, lets tokenize various corpses.
```{r tokenizationdata, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
#Generate unigram, bigram, trigram & quadgram for blog dataset
blog.unigram <- gramTopCount(corpusBlog, 1)
blog.digram <- gramTopCount(corpusBlog, 2)
blog.trigram <- gramTopCount(corpusBlog, 3)
blog.quadgram <- gramTopCount(corpusBlog, 4)
#Generate unigram, bigram, trigram & quadgram for news dataset
news.unigram <- gramTopCount(corpusNews, 1)
news.digram <- gramTopCount(corpusNews, 2)
news.trigram <- gramTopCount(corpusNews, 3)
news.quadgram <- gramTopCount(corpusNews, 4)
#Generate unigram, bigram, trigram & quadgram for tweet dataset
tweet.unigram <- gramTopCount(corpusTweet, 1)
tweet.digram <- gramTopCount(corpusTweet, 2)
tweet.trigram <- gramTopCount(corpusTweet, 3)
tweet.quadgram <- gramTopCount(corpusTweet, 4)
#Generate unigram, bigram, trigram & quadgram for all dataset
part.unigram <- gramTopCount(corpusPart, 1)
part.digram <- gramTopCount(corpusPart, 2)
part.trigram <- gramTopCount(corpusPart, 3)
part.quadgram <- gramTopCount(corpusPart, 4)
```

# Visualization

## Histogram

### Function

```{r gramPlotQuadFunction, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
gramPlotQuad <-
        function(tweetgram,
                 bloggram,
                 newsgram,
                 partgram,
                 title = "NoGram",
                 TopCount = 10) {
                gtweet <-
                        ggplot(head(tweetgram, TopCount),
                               aes(x = reorder(Word, -Frequency), y = Frequency)) +
                        geom_bar(stat = "Identity", fill = "#1dcaff") +
                        geom_text(aes(label = Frequency),
                                  hjust = 1,
                                  angle = 90) +
                        xlab("Word") +
                        ggtitle(paste("Tweets", title)) +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1))
                gblog <-
                        ggplot(head(bloggram, TopCount),
                               aes(x = reorder(Word, -Frequency), y = Frequency)) +
                        geom_bar(stat = "Identity", fill = "orange") +
                        geom_text(aes(label = Frequency),
                                  hjust = 1,
                                  angle = 90) +
                        xlab("Word") +
                        ggtitle(paste("Blogs", title)) +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1))
                gnews <-
                        ggplot(head(newsgram, TopCount),
                               aes(x = reorder(Word, -Frequency), y = Frequency)) +
                        geom_bar(stat = "Identity", fill = "#87F717") +
                        geom_text(aes(label = Frequency),
                                  hjust = 1,
                                  angle = 90) +
                        xlab("Word") +
                        ggtitle(paste("News", title)) +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1))
                gall <-
                        ggplot(head(partgram, TopCount),
                               aes(x = reorder(Word, -Frequency), y = Frequency)) +
                        geom_bar(stat = "Identity", fill = "#F6358A") +
                        geom_text(aes(label = Frequency),
                                  hjust = 1,
                                  angle = 90) +
                        xlab("Word") +
                        ggtitle(paste("All Source", title)) +
                        theme(axis.text.x = element_text(angle = 45, hjust = 1))
                grid.arrange(gtweet,
                             gblog,
                             gnews,
                             gall,
                             ncol = 2,
                             nrow = 2)
                
        }


```


### Visualization

```{r loadmain data, message=FALSE, warning=FALSE, include=FALSE}
#load dataset
load("/Users/VirKrupa/Documents/01_Courses/40_DataScience_Capstone/Assignment/DataScience_CapStone/00_Data/final_plot_Data.RData")
```

Lets Plot th graphs

#### Top 10 UniGrams across all datasets

```{r gramPlotQuadVis1, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
##ploting
g1 <- gramPlotQuad(
        tweetgram = tweet.unigram,
        bloggram = blog.unigram,
        newsgram = news.unigram,
        partgram = part.unigram,
        title = "UniGram"
)
```

```{r gramPlotQuadVis1plot, echo=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}
grid.arrange(g1)
```


#### Top 10 Bigrams across all datasets

```{r gramPlotQuadVis2, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
##ploting
g2 <- gramPlotQuad(
        tweetgram = tweet.digram,
        bloggram = blog.digram,
        newsgram = news.digram,
        partgram = part.digram,
        title = "BiGram"
)
```

```{r gramPlotQuadVis2plot, echo=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}
grid.arrange(g2)
```

#### Top 10 TriGrams across all datasets

```{r gramPlotQuadVis3, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
##ploting
g3 <- gramPlotQuad(
        tweetgram = tweet.trigram,
        bloggram = blog.trigram,
        newsgram = news.trigram,
        partgram = part.trigram,
        title = "TriGram"
)
```

```{r gramPlotQuadVis3plot, echo=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}
grid.arrange(g3)
```

#### Top 10 QuadGrams across all datasets

```{r gramPlotQuadVis4, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
##ploting
g4 <- gramPlotQuad(
        tweetgram = tweet.quadgram,
        bloggram = blog.quadgram,
        newsgram = news.quadgram,
        partgram = part.quadgram,
        title = "QuadGram"
)
```

```{r gramPlotQuadVis4plot, echo=FALSE, fig.height=9, fig.width=10, message=FALSE, warning=FALSE}
grid.arrange(g4)
```

### Discussion

All application needs different type of modeling as distribution of various grams differes.

## WordCloud

### Function

```{r cloudPlotQuadFunction, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
cloudPlotQuad <-
        function(tweetgram,
                 bloggram,
                 newsgram,
                 partgram,
                 Type = "UniGram") {
                par(mfrow = c(2, 2))
                wordcloud(
                        as.character(tweetgram$Word),
                        tweetgram$Frequency,
                        min.freq = 10,
                        max.words = 75,
                        colors = brewer.pal(11, "Paired"),
                        random.order = F,
                        random.color = T,
                        rot.per = .15,
                        scale = c(4, 0.5)
                )
                wordcloud(
                        as.character(bloggram$Word),
                        bloggram$Frequency,
                        min.freq = 10,
                        max.words = 75,
                        colors = brewer.pal(11, "Paired"),
                        random.order = F,
                        random.color = T,
                        rot.per = .15,
                        scale = c(4, 0.5)
                )
                wordcloud(
                        as.character(newsgram$Word),
                        newsgram$Frequency,
                        min.freq = 10,
                        max.words = 75,
                        colors = brewer.pal(11, "Paired"),
                        random.order = F,
                        random.color = T,
                        rot.per = .15,
                        scale = c(4, 0.5)
                )
                wordcloud(
                        as.character(partgram$Word),
                        partgram$Frequency,
                        min.freq = 10,
                        max.words = 75,
                        colors = brewer.pal(11, "Paired"),
                        random.order = F,
                        random.color = T,
                        rot.per = .15,
                        scale = c(4, 0.5)
                )
                mtext(
                        paste0("WordCloud of ", Type, "'s"),
                        side = 2,
                        line = -2,
                        outer = TRUE,
                        col = "blue",
                        cex = 1.4
                )
                mtext(
                        "News                                          Tweet",
                        side = 2,
                        line = -3,
                        outer = TRUE,
                        col = "black",
                        cex = 1.2
                )
                mtext(
                        "All Source                                     Blog",
                        side = 4,
                        line = -2,
                        outer = TRUE,
                        col = "black",
                        cex = 1.2
                )
                
                par(mfrow = c(1, 1))
        }
```

### Visualization
Lets Plot th graphs

#### WordCloud of UniGrams across all datasets

```{r cloudPlotQuad1Plot, echo=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}
w1u <- cloudPlotQuad(
        tweetgram = tweet.unigram,
        bloggram = blog.unigram,
        newsgram = news.unigram,
        partgram = part.unigram,
        Type = "UniGram"
)
```



#### WordCloud of BiGrams across all datasets

```{r cloudPlotQuad2Plot, echo=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE}
w2u <- cloudPlotQuad(
        tweetgram = tweet.digram,
        bloggram = blog.digram,
        newsgram = news.digram,
        partgram = part.digram,
        Type = "BiGram"
)
```

### Discussion

All application needs different type of modeling as distribution of various grams differes.


# Conclusion

Future application Devlopment.


